State of the Art in \\ {\ttlit Twitter Sentiment Analysis}

### 2015-01-22 paper/chapters/4_classification.tex
paper: remove typo
paper: further techniques

where $c_j \in \lbrace 1, -1\rbrace$ (in sentiment classification $1$ would denote "positive" and correspondingly $-1$ stands for "negative" sentiment). The actual classification of document $d$ is done, by determining on which side of $\vec{omega}$ its document vector $\vec{d}$ falls on.

\subsubsection*{Further techniques}

TODO

>>>>

where $c_j \in \lbrace 1, -1\rbrace$ (in sentiment classification $1$ would denote "positive" and correspondingly $-1$ stands for "negative" sentiment). The actual classification of document $d$ is done, by determining on which side of $\vec{\omega}$ its document vector $\vec{d}$ falls on.

\subsubsection*{Further techniques}
Beside Na\"ive Bayes and Support Vector Machines various other machine learning techniques such as Character based N-gram model, Maximum entropy, Random Forest and J48 exist and are just mentioned here for the sake of completeness, a comprehensive view of other machine learning techniques is beyond the scope of this survey.
